An indexed construction of semi-cubical types

### 2021-07-06 paper/paper.tex
[paper] Clean up two more figures

% Subbox, sublayer, and subcube
\newcommand{\downbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
\newcommand{\downlayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
\newcommand{\downcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}

% Coherence conditions
\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}

@@

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[h!]
\tabularx{\textwidth}{@{} l c c X @{}}\toprule}
{\endtabularx\hrule\caption{#1}\endtable}

% A block in the eqntable environment
\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}

@@

\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{properfiller}_{#1}}
\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
\newcommand{\border}[1]{\mathsf{border}_{#1}}
\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
\newcommand{\mygroundedcube}[1]{\mathsf{groundedcube}_{#1}}
\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

@@

The definition is dispatched over Figures~\ref{fig:barecubicalsetstructurecore}, \ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}. It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations. All are mutually defined as types of the target language ETT. Note that such relational structure, cubes and boxes are relative to a universe. Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type. The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory). Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.

@@

  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}

@@

  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}

@@

  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))($c_L$)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))($c_R$)))}}

@@

  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{$b_\epsilon$}

@@

Note that the components of an $n$-box or $n$-tube are tuples associated to the left. For cubes, the components can be associated to the left, and we call this a full $n$-cube or to the right, which we call grounded $n$-cube, and which corresponds to ``complete'' partial cubes, i.e. to partial cubes over the empty box. Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).

@@

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \multicolumn{4}{c}{\mbox{Full (non-truncated) cubical sets with degeneracies}}                                         \\
          \\
          \mycubset{l}        &                          & :      & \sort{l+1}                                                   \\
          \mycubset{l}        &                          & \defeq & \mycubsetfrom{l}{0}(\star)                                   \\
          \\
          \mycubsetfrom{l}{n} & (D:\partialcubset{l}{n}) & :      & \sort{l+1}                                                   \\
          \mycubsetfrom{l}{n} & D                        & \defeq & \Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)
        \end{array}
      $
    }}
  \caption{Definition of a bare cubical set (coinductive structure)}
  \label{fig:barecubicalset}
\end{figure*}

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \multicolumn{4}{c}{\mbox{\textit{Type of full $n$-cubes}}}                                                                                                                         \\
          \\
          \myfullcube{l}^{n}     & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}                                                             & :      & \sort{l}                                          \\
          \myfullcube{l}^{n}     & (D,E)                                                                                        & \defeq & \Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d) \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{Type of $n$-tubes}}}                                                                                                                              \\
          \\
          \tube{l}^{n}           & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
          \tube{l}^{n}           & D                                                                                            & \defeq & \mybox{l}{n+1,n}(D)                               \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{Type of grounded $n$-cubes}}}                                                                                                                     \\
          \\
          \mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
          \mygroundedcube{l}^{n} & (D,E)                                                                                        & \defeq & \mycube{l}{n,0}(D)(E)(\star)                      \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{Type of fillers of some $n$-box}}}                                                                                                                \\
          \\
          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))                                      & :      & \sort{l}                                          \\
          \propercube{l}^{n}     & (D,E)~d                                                                                      & \defeq & E.\mathsf{rel}(d)                                 \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{Border of a grounded $n$-cube}}}                                                                                                                  \\
          \\
          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                     & :      & \myfullbox{l}{n}(\hd(D))                          \\
          \border{l}^{n}         & D~c                                                                                          & \defeq & \border{l}^{n,0}(D)(\star)(c)                     \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{where the border of partial cubes is defined by}}}                                                                                                \\
          \\
          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}{n}(\hd(D))                          \\
          \border{l}^{n,p,[p=n]} & D~d~c                                                                                        & \defeq & d                                                 \\
          \border{l}^{n,p,[p<n]} & D~d~(b,c)                                                                                    & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)                     \\
        \end{array}
      $
    }}
  \caption{Standard derived notions}
  \label{fig:macros}
\end{figure*}

>>>>

% Subbox, sublayer, and subcube
\newcommand{\downbox}[2][2=]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
\newcommand{\downlayer}[2][2=]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
\newcommand{\downcube}[2][2=]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
\newcommand{\myfullbox}[2][2=]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}

% Coherence conditions
\newcommand{\cohbox}[2][2=]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
\newcommand{\cohcube}[2][2=]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
\newcommand{\cohlayer}[2][2=]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}

% Border
\newcommand{\border}[1][1=]{\ensuremath{\mathsf{border}_{#1}}}

@@

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[h!]
\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
{\endtabularx\hrule\caption{#1}\endtable}

% A block in the eqntable environment
\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}

@@

\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{properfiller}_{#1}}
\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
\newcommand{\mygroundedcube}[1]{\mathsf{groundedcube}_{#1}}
\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

@@

The definition is dispatched over Figures~\ref{fig:barecubicalsetstructurecore}, \ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}. It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations. All are mutually defined as types of the target language ETT. Note that such relational structure, cubes and boxes are relative to a universe. Note the presence of a coherence condition \cohbox{l} to ensuring that both sides of the equality in \downlayer{l} and \downcube{l} are in the same type. The proof of \cohbox{l} itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory). Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning \downbox{l} nor \cohbox{l} anymore.

@@

  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\;\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}

@@

  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\mathsf{rel}(d)}

@@

  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))}}

@@

  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}

@@

Note that the components of an $n$-box or $n$-tube are tuples associated to the left. For cubes, the components can be associated to the left, and we call this a full $n$-cube or to the right, which we call grounded $n$-cube, and which corresponds to ``complete'' partial cubes, i.e. to partial cubes over the empty box. Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see \border).

@@

\begin{eqntable}{Definition of a bare cubical set (coinductive structure)}
  \mc{Full (non-truncated) cubical sets with degeneracies}
  \eqnline{\mycubset{l}}{}{:}{\sort{l+1}}
  \eqnline{\mycubset{l}}{}{\defeq}{\mycubsetfrom{l}{0}(\star)}
  \\
  \eqnline{\mycubsetfrom{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l+1}}
  \eqnline{\mycubsetfrom{l}{n}}{D}{\defeq}{\Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)}
\end{eqntable}

\begin{eqntable}{Standard derived notions}
  \mc{Type of full $n$-cubes}

  \eqnline{\myfullcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}

  \eqnline{\myfullcube{l}^{n}}{(D,E)}{\defeq}{\Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d)}

  \\ \mc{Type of $n$-tubes}

  \eqnline{\tube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
  \eqnline{\tube{l}^{n}}{D}{\defeq}{\mybox{l}{n+1,n}(D)}

  \\ \mc{Type of grounded $n$-cubes}

  \eqnline{\mygroundedcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
  \eqnline{\mygroundedcube{l}^{n}}{(D,E)}{\defeq}{\mycube{l}{n,0}(D)(E)(\star)}

  \\ \mc{Type of fillers of some $n$-box}

  \eqnline{\propercube{l}^{n}}{(D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))}{:}{\sort{l}}

  \eqnline{\propercube{l}^{n}}{(D,E)~d}{\defeq}{E.\mathsf{rel}(d)}

  \\ \mc{Border of a grounded $n$-cube}

  \eqnline{\border{l}^{n}}{(D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))}{:}{\myfullbox{l}{n}(\hd(D))}

  \eqnline{\border{l}^{n}}{D~c}{\defeq}{\border{l}^{n,0}(D)(\star)(c)}

  \\ \mc{where the border of partial cubes is defined by}

  \eqnline{\border{l}^{n,p}}{(D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d))}{:}{\myfullbox{l}{n}(\hd(D))}

  \eqnline{\border{l}^{n,p,[p=n]}}{D~d~c}{\defeq}{d}

  \eqnline{\border{l}^{n,p,[p<n]}}{D~d~(b,c)}{\defeq}{\border{l}^{n,p+1}(D)(d,b)(c)}
\end{eqntable}
